Word Learning as Network Growth: A Cross-linguistic Analysis

### 2019-01-09 cogsci/cogsci.Rmd
new modif on manuscript

Figures (\ref{fig:data_all}, middle and right graphs) show the predictions of the models. Both model 1 and model 2 fit reseanaby well the experimental data in both children and adults. In particular, they both correcly predict the relative recognition accuacy accross conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.

For Model 1, the fitted noise parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`]\footnote{95 \% Confidence intervals.} for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults. It explained the majority of the variance ($R^2=$ `r R2_model1`). For model 2, children had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`]. Adults had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`]. The model explain almost all the variance ($R^2=$ `r R2_model2`), and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`]. Interestingly, despite the fact that Model 1 used only one degree of freedom, it captures the data variance almost as well as Model 2 (which used two degrees of freedom).

@@

Here maybe be more precise about what the model does (providing a summary in prose of the main results )

Subsequent studies have shown that   To account for this phenomenon, we proposed a model where words and their semantic referents are both encoded in a probabilistic fashion.  A pair of words may be encoded simultaneousely, but successful recognition depends both on the perceptual distance between the words and on the degree of uncertainty of their encoding. These predictions explained learning patterns both within and across developmental stages, respectively.

>>>>

Figures (\ref{fig:data_all}, middle and right graphs) show the predictions of the models. Both model 1 and model 2 fit reseanaby well the experimental data in both children and adults. In particular, they both correcly predict the relative recognition accuacy accross conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels. Note, however, that both model predict a

For Model 1, the fitted uncertainty parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`]\footnote{95 \% Confidence intervals.} for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults. The model explained the majority of the variance ($R^2=$ `r R2_model1`). For model 2, children had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`]. Adults had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`], and a concept-specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`]. The model explained almost all the variance ($R^2=$ `r R2_model2`).  Interestingly, despite the fact that Model 1 used only one degree of freedom, it captures the data variance almost as well as Model 2 (which used two degrees of freedom).

@@

...To account for this phenomenon, we proposed a model where words and their semantic referents are both encoded in a probabilistic fashion.  A pair of words may be encoded simultaneousely, but successful recognition depends both on the perceptual distance between the words and on the degree of uncertainty of their encoding. These predictions explained learning patterns both within and across developmental stages, respectively.

### 2019-01-09 cogsci/cogsci.tex
new modif on manuscript

\caption{\label{fig:illus} An illustration of the probabilsitic account using simulated data. Words are category distributions over the perceptual space, encoded with different degrees of uncertainty. Accuracy experesses the extent to which a given sound instance indicates a unique underlying category. The values vary between 0.5 (total overlap between the distributions) and 1 (no overalp). Accuracy is low when the perceptual distance between labels is small relative to the category variance. Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
\end{figure}
\end{CodeChunk}

@@

The object-sound pairings were randomized across participants, as was
the order of the conditions (except for the catch condition which was
always placed in the middle of the testing sequence). We also randomized
the on-screen position (left vs.~right) of the two pictures on each
testing trial. The procedure for preschoolers and adults were identical
except that preschoolers were accompagnied by an experimenter and used a
tablet, whereas adults used their local computers to complete the
experiment online.

@@

We fit the analystical expression (equation 2) to the participants'
responses in each age group. The values of \(\Delta s\) and \(\Delta o\)
were set based on data from the similarity judgment task (described in
the stimuli sub-section). We used two models: \textbf{model 1} fit only
one parameter (\(\sigma = \sigma_C =\sigma_L\)), and \textbf{model 2}
fit two parameters (\(\sigma_C \neq \sigma_L\)). The values of the
parameters were derived using weighted least-squares estimates.

@@

First we analyzed the experimental results shown in Figure (XX, left),
using a mixed-effects logistic regression with sound and object
distances as fixed effects, and with a maximal random effects strcuture
(Barr, Levy, Scheepers, \& Tily, 2013). Results are shown in Table XX.
We found a main effect of sound distance on the accuray of learning in
both children and adults, thus replicating previous findings. We also
found a main effect of object distance, thus confirming the new
prediction of our model.

@@

Figures XX (middle and right graphs) show the predictions of the models.
Both model 1 and model 2 fit reseanaby well the experimental data in
both children and adults. In particular, they both correcly predict the
relative recognition accuacy accross conditions: the pair of words that
differ on both the object and sound levels were the easiest to learn,
followed by the pairs of words that differ on only one level, then the
pair of words that are similar on both levels.

For Model 1, the fitted noise parameter was \(\sigma =\) 0.63 {[}0.53,
0.73{]} for preschoolers, and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for
adults. It explained the majority of the variance (\(R^2=\) 0.94). For
model 2, children had a sound specific noise of \(\sigma_S =\) 0.9
{[}0.68, 1.11{]}, and a concept specific noise of \(\sigma_C =\) 0.29
{[}0.1, 0.49{]}. Adults had a sound specific noise of \(\sigma_S =\)
0.16 {[}0.05, 0.28{]}. The model explain almost all the variance
(\(R^2=\) 0.96), and a concept specific noise of \(\sigma_C =\) 0.14
{[}0.05, 0.23{]}. Note that, despite the fact that Model 1 used only one
degree of freedom, it captures the data variance almost as well as Model
2 which used two degrees of freedom.

@@

Here maybe be more precise about what the model does (providing a
summary in prose of the main results )

Subsequent studies have shown that To account for this phenomenon, we
proposed a model where words and their semantic referents are both
encoded in a probabilistic fashion. A pair of words may be encoded
simultaneousely, but successful recognition depends both on the
perceptual distance between the words and on the degree of uncertainty
of their encoding. These predictions explained learning patterns both
within and across developmental stages, respectively.

>>>>

\caption{\label{fig:illus} An illustration of the probabilsitic account of similar word learning using simulated data. Words are category distributions over the perceptual space, encoded with different degrees of uncertainty. Accuracy experesses the extent to which a given sound instance indicates a unique underlying category. The values vary between 0.5 (total overlap between the distributions) and 1 (no overalp). Accuracy is low when the perceptual distance between labels is small relative to the category variance. Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
\end{figure}
\end{CodeChunk}

@@

The object-sound pairings were randomized across participants, as was
the order of the conditions (except for the catch condition which was
always placed in the middle of the testing sequence). We also randomized
the on-screen position (left vs.~right) of the two pictures on each
testing trial.

The procedure adults were identical except to that of preschool
children, except that preschoolers were accompagnied by an experimenter
and used a tablet, whereas adults used their local computers to complete
the experiment online.

@@

We fit the probability function (equation 2) to the participants'
responses in each age group. The values of \(\Delta s\) and \(\Delta o\)
were set based on data from the similarity judgment task (described in
the stimuli sub-section). We used two models: \textbf{model 1} fit only
one parameter (\(\sigma = \sigma_C =\sigma_L\)), and \textbf{model 2}
fit two parameters (\(\sigma_C \neq \sigma_L\)). The values of the
parameters were derived using weighted least-squares estimates.

@@

We first analyzed the experimental results shown in Figure
(\ref{fig:data_all}, left), using a mixed-effects logistic regression
with sound and object distances as fixed effects, and with a maximal
random effects strcuture (Barr, Levy, Scheepers, \& Tily, 2013). Results
are shown in Table 1. We found a main effect of sound distance on the
accuray of learning in both children and adults, thus replicating
previous findings. We also found a main effect of object distance, thus
confirming the new prediction of our model.

@@

Figures (\ref{fig:data_all}, middle and right graphs) show the
predictions of the models. Both model 1 and model 2 fit reseanaby well
the experimental data in both children and adults. In particular, they
both correcly predict the relative recognition accuacy accross
conditions: the pair of words that differ on both the object and sound
levels were the easiest to learn, followed by the pairs of words that
differ on only one level, then the pair of words that are similar on
both levels. Note, however, that both model predict a

For Model 1, the fitted uncertainty parameter was \(\sigma =\) 0.63
{[}0.53, 0.73{]}\footnote{95 \% Confidence intervals.} for preschoolers,
and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for adults. The model explained
the majority of the variance (\(R^2=\) 0.94). For model 2, children had
a label-specific uncertainty of \(\sigma_S =\) 0.9 {[}0.68, 1.11{]}, and
a concept-specific uncertainty of \(\sigma_C =\) 0.29 {[}0.1, 0.49{]}.
Adults had a sound specific noise of \(\sigma_S =\) 0.16 {[}0.05,
0.28{]}, and a concept-specific noise of \(\sigma_C =\) 0.14 {[}0.05,
0.23{]}. The model explained almost all the variance (\(R^2=\) 0.96).
Interestingly, despite the fact that Model 1 used only one degree of
freedom, it captures the data variance almost as well as Model 2 (which
used two degrees of freedom).

@@

\ldots{}To account for this phenomenon, we proposed a model where words
and their semantic referents are both encoded in a probabilistic
fashion. A pair of words may be encoded simultaneousely, but successful
recognition depends both on the perceptual distance between the words
and on the degree of uncertainty of their encoding. These predictions
explained learning patterns both within and across developmental stages,
respectively.
